Kaggle-in-class Data Challenges Can Boost Student Learning

### 2019-09-24 paper-kaggle.Rmd
doen with revisions

Students received clean data ready for modelling as we only aimed to examine students ability to apply covered material. If the instructor's aim is rather to mimic real-life situation when prior to modelling/forecasting data needs to be processed and cleaned, then this task should be left to students. In our opinion, this approach is more suitable for advanced classes.

@@

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|p{15cm}|}\hline
Label & Question \\\hline
Q1 & I found the data competition is great fun.\\\hline
Q2 & Taking part in the data competition contributed a lot to my engagement with the subject.\\\hline
Q3 & Taking part in the data competition improved my confidence in my understanding of the covered material.\\\hline
Q4 & Taking part in the data competition improved my confidence in my success in the final exam.\\\hline
Q5 & Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.\\\hline
Q6 & I feel that the required time investment in the data competition was worthy. \\\hline
\end{tabular}
\end{center}
\caption{Questions asked in the survey of competition participants.}
\label{survey_Q}
\end{table}

@@

Finding a suitable data set for a competition can be a challenge. The criteria for a good data set are:

1. the full set is not available to the students, to avoid cheating.
2. the data is not too easy, or too hard, to model, so that there is some discriminatory ower in the results.
3. contains some challenges, that make standard off-the-shelf modeling less successful, like different variable types that need processing or transforming, some outliers, large number of variables. 
4. If it is a classification challenge, it will work better with relatively balanced classes, because the overall accuracy is the easiest metric to use.

@@

It may be recommended to limit students to one submission per day. It encourages students to think about more efficient improvement of their model before the next submission. It also prevents the student spending too much time building and submitting models. Some students will become so engaged in the competition tha they might neglect their other coursework. About halfway throug hthe coompetition 
<!--We also believe that it is better to start the competition in the second half of the semester and finish it two to one week before the end of the semester. It allows to cover many different statistical methods that students may apply during the competition. Finishing some time before the end of the semester reduces students anxiety at the end of the semester and the approaching exams. -->

@@

@@

<!--
https://github.com/dicook/paper-quoll. 
-->
Information on setting up a Kaggle InClass challenge can be found at https://www.kaggle.com/about/inclass/overview.

>>>>

<!-- 
Students received clean data ready for modelling as we only aimed to examine students ability to apply covered material. If the instructor's aim is rather to mimic real-life situation when prior to modelling/forecasting data needs to be processed and cleaned, then this task should be left to students. In our opinion, this approach is more suitable for advanced classes.  
-->

@@

\begin{table}[b!]
\begin{center}
\begin{tabular}{|l|p{15cm}|}\hline
Label & Question \\\hline
Q1 & I found the data competition is great fun.\\\hline
Q2 & Taking part in the data competition contributed a lot to my engagement with the subject.\\\hline
Q3 & Taking part in the data competition improved my confidence in my understanding of the covered material.\\\hline
Q4 & Taking part in the data competition improved my confidence in my success in the final exam.\\\hline
Q5 & Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.\\\hline
Q6 & I feel that the required time investment in the data competition was worthy. \\\hline
\end{tabular}
\end{center}
\caption{Questions asked in the survey of competition participants.}
\label{survey_Q}
\end{table}

@@

@@

The kaggle service provides some data sets, primarily for student self-learning. These are not suitable for use in a class challenge, because all the data is available, and solutions are also provided. We recommend providing your own data for the class challenge.  Finding a suitable data set for a competition can be a difficult task. The criteria for a good data set are:

1. the full set is not available to the students, to avoid cheating.
2. the data is not too easy, or too hard, to model so that there is some discriminatory power in the results.
3. data should be relatively clean, to the point where the instructor has tested that a model can be fitted.
4. contains some challenges, that make standard off-the-shelf modeling less successful, like different variable types that need processing or transforming, some outliers, large number of variables. 
5. if it is a classification challenge, it will work better with relatively balanced classes, because the overall accuracy is the easiest metric to use.

@@

It may be recommended to limit students to one submission per day. It encourages students to think about more efficient improvement of their model before the next submission. It also prevents the student spending too much time building and submitting models. Some students will become so engaged in the competition that they might neglect their other coursework. About halfway through the coompetition, students might be allowed to form teams, to learn how averaging models can boost performance.

@@

Along with the competition, students were expected to submit a report that explained their modeling strategy, and what they had learned about the data beyond the modeling. The overall score for this part of the course was a combination of the mark for their report and their performance in the challenge. In both courses this accounted for 10% of the final mark.

@@

<!--
https://github.com/dicook/paper-quoll. 
-->
